Robot programming for dummies

### 2013-05-17 paper.tex
More work

\title {Why robot programming is hard}
\author {Tessa Lau \\
Willow Garage \\
Menlo Park, CA USA \\
{\tt tlau@willowgarage.com}
}
\maketitle

>>>>

\title {Robot programming for dummies}
\author {Tessa Lau \\
Willow Garage \\
Menlo Park, CA USA \\
{\tt tlau@willowgarage.com}
}
\maketitle

I never thought I would be a roboticist. In grad school, our robotics team spent months teaching little robot dogs to play soccer and solving other seemingly simple problems. I was better off in the world of software, I thought, where the systems I built could make a real difference in people's lives. Software robots would automate repetitive tasks in computer use and free people from mundane work. End user programming would enable millions of ordinary computer users to customize and adapt systems to their own needs.

But that world is changing. People aren't primarily sitting in front of their computers, pushing bits around. Nowadays, innovation is happening in the real world, where computing is being used to effect physical change in the world around us. The past decades have seen industrial robots increase manufacturing efficiency on the factory floor. Even more, we are now seeing robots popping up in the consumer space. Robotic vacuum cleaners are changing the way we clean our homes. Robotic lawnmowers keep the yard tidy without having to lift a finger. Nest's robotic thermostat learns your habits and keeps your home at the optimal temperature.

All these innovations have become possible through multiple advances: in sensor technology, which robots use to perceive the world around them; in planning and navigation, which enable robots to move around in the world unaided; in human-safe motion controllers, which let robots move their limbs without endangering humans around them; in the ROS open source robot operating system, which enables roboticists to build on each others' work without starting from scratch; and many more advances in the broader field of robotics.

Yet despite all of these advances, the holy grail of personal robotics remains elusive. When will we have our own Rosie the Robot (from the Jetsons cartoon) to take over housekeeping chores? Since starting work at Willow Garage and becoming immersed in the challenges of the robotics industry, I now believe that the limiting factor is end user programming.
